A large-scale analysis of racial disparities in police stops across the United

### 2019-12-12 lib/paper_results.Rmd
reformatting for paper

```{r search_rates_summary}
pfs$summary_table
```

@@

```{r veil_of_darkness-appendix_mods}
bind_rows(
  vod$dst %>%
    select(-data, -base_controls) %>% 
    mutate(model = "DST"),
  vod$full$coefficients %>%
    select(-data, -base_controls) %>% 
    mutate(model = "Full year")
) %>%
  arrange(model, agency_control, interact_time_loc, spline_degree) %>% 
  select(model, agency, is_dark, std_error, p_value, everything()) %>%
  kable()
```

>>>>

total: `r pfs$summary_table$Stops %>% str_replace_all(",", "") %>% as.numeric() %>% sum %>% comma_num()`

```{r search_rates_summary}
pfs$summary_table %>% 
  mutate(agency = if_else(City == "--", "state", "city")) %>% 
  group_by(agency) %>% 
  mutate(ct = 1:n()) %>% 
  ungroup() %>% 
  select(-agency) %>% 
  select(ct, everything()) %>% 
  kable("latex")
```

@@

```{r veil_of_darkness-appendix_mods}
vod$dst %>%
  select(-data, -base_controls) %>%
  arrange(agency_control, interact_time_loc, spline_degree) %>% 
  select(agency, is_dark, std_error, p_value, everything()) %>%
  kable()
```
